\subsection*{get\_K\_clrd\_noise} \label{fun:get_K_clrd_noise}


\textbf{Syntax}
\\  \texttt{function [Cn, Cn\_vec] = get\_K\_clrd\_noise(NN, a, b,
noisevar)}

\textbf{Description}
\\ Function returns the noise part of covariance matrix, when the
 coloured noise on the output of the system is known.
 This covariance matrix should be added to its function part. The
 function folows the derivation in {[}1{]} and differs a bit from
{[}2{]}.
\\ Idea:
\\ AR part (ai-s) :
\\ first na elements of the covariance matrix calculated using Yule-Walker
\\ equations, the rest of them (na+1 .. NN) computed iteratively
\\ MA part (bi-s) :
\\ the elements of covariance matrix up to bn are calculated, the rest of
\\ them equals 0
\\ Notes:
\\ (1) K(tau) = K(i,j), where $|i-j|=|j-i|=tau$
\\ (2) Function is not compatible with the current version of the GPML
\\ toolbox.
\\ (3) Function uses the function TOEPLITZ.
\\
\\ Inputs:
\\ NN .. size of the covariance matrix (number of training data)
\\ a ... vector of AR elements of correlated-noise (1 a\_1 a\_2 .. a\_na)
\\ b ... vector of MA elements of correlated-noise (b\_0 b\_1 b\_2 .. b\_nb)
\\    usually b\_0=0
\\ noisevar ... noise variance sigma\_e$^2$
\\ Outputs:
\\ Cn .. noise part of the covariance matrix
\\ Cn\_vec .. elements of the covariance matrix in a vector

\textbf{See Also}
\\ {[}1{]} K. Azman, J. Kocijan, Identifikacija dinamiènega sistema z znanim modelom
\\ šuma z modelom na osnovi Gaussovih procesov, n: B. Zajc, A. Trost (eds.)
\\ Zbornik petnajste mednarodne Elektrotehniške in raèunalniške konference
\\ ERK 2006, 25.-27.09., Portorož, Slovenija, 2006, Vol. A, pp. 289--292,
\\ 2006.  (in Slovene)
\\ {[}2{]} R. Murray-Smith and A. Girard. Gaussian Process Priors with ARMA
\\ noise models. In Proceedings: Irish Signals and Systems Conference,
\\ 147-153, Maynooth, 2001.
