\subsection*{gpSD00ran}  \label{fun:gpSD00ran}


\textbf{Syntax}
\texttt{function [mu, S2, invQ] = gpSD00ran(X, input, target, targetvariance, derivinput, derivtarget, derivvariance, test, SigmaX)}

\textbf{Description}
\\ This function computes the predictive mean and variance at test input for
 the LMGP model with the covariance function as sum of covSEard
and  covNoise.  The prediction and propagation of variance is done
by this
 routine. When test data are given, then (marginal) Gaussian
predictions  are computed, whose mean and (noise free) variance
are returned.
\\
\\ Inputs:
\\ X       ..  a (column) vector (of size D+2) of hyperparameters
\\ input   ..  a n by D matrix of training inputs
\\ target  ..  a (column) vector (of size n) of targets
\\ targetvariance  ..  a (column) vector (of size n) of variances of
 targets unknown variances
 \\ \tab are indicated by NaN -- these are then
   replaced by the noise term in the covariance
   \\ \tab  function
\\ derivinput  ..  an n by D matrix of training inputs at which we have
\\   derivative information (not necessarily the same as 'input').
\\ derivtarget  ..  an n by D matrix of partial derivatives at 'derivinput',
 w.r.t. each input
\\ derivvariance  ..  an n by D\^2 matrix, where each row is the elements of
 the covariance
 \\ \tab  matrix associated with the appropriate derivtarget
\\ test    ..  a nn by D matrix of test inputs
\\ SigmaX  ..  covariance of the test input
\\ Outputs:
\\ mu      ..  a (column) vector (of size nn) of prediced means
\\ S2      ..  a (column) vector (of size nn) of predicted variances
\\ invQ    ..  the inverse or covariance matrix.
\\
\\ (C) Copyright 1999 - 2003, Carl Edward Rasmussen (2003-07-24).
\\ derivative adaptation, Roderick Murray-Smith (2003-07-25). Can now cope
\\ with a number of derivative observations independent of the number of
\\ function observations. It has seperate noise level for the derivative
\\ observations.
\\ Variance propagation upgrade, Jus Kocijan, 2003

\textbf{Examples}
\\ demo\_example\_lmgp\_simulation.m

\textbf{See Also}
\\ SIMULLMGP00NAIVE SIMULLMGP00MCMC, MINIMIZE, GPSD00
